Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-20 optim.qmd
sec 3 update text

The jellyfish optimiser (JSO) mimics the natural movements of jellyfish,
which include passive and active motions driven by ocean currents and
their swimming patterns, respectively. In the context of optimization,
these movements are abstracted to explore the search space in a way that
balances exploration (searching new areas) and exploitation (focusing on
promising areas). The algorithm aims to find the optimal solution by
adapting the jellyfish's behaviour to navigate towards the best solution
over iterations [@chou_novel_2021].

To understand what the jellyfish optimizer is doing in the context of
Projection Pursuit, we first start with a current projection (the
starting point). Then, we evaluate this projection using an index
function, which tells us how good the current projection is. We then
move the projection in a direction determined by the 'best jelly' and
random factors, influenced by how far along we are in the optimization
process (the trial $i$ and `max.tries`). Occasionally, we might explore
completely new directions like a jellyfish might with ocean currents.
Then, we compare new potential projections to our current one. If
they're better, we adopt them; if not, we stick with our current
projection. This process continues and iteratively improves the
projection, until we reach the maximum number of trials.

>>>>

JSO mimics the natural movements of jellyfish, which include passive and active motions driven by ocean currents and
their swimming patterns, respectively. In the context of optimization, these movements are abstracted to explore the search space in a way that
balances exploration (searching new areas) and exploitation (focusing on
promising areas). The algorithm aims to find the optimal solution by
adapting the behaviour of jellyfish to navigate towards the best solution over iterations [@chou_novel_2021].

To solve the optimisation problem embedded in the PP guided tour, a starting projection, an index function and the maximum number of iterations are provided as input. Then, the current projection is evaluated by the index function. The projection is then moved in a direction determined by a random factor, influenced by how far along we are in the optimization process. Occasionally, we might explore completely new directions like a jellyfish might with ocean currents. A new projection is accepted if it is an improvement compared to the current one, rejected otherwise.
This process continues and iteratively improves the projection, until the pre-specified maximum number of trials is reached.

### 2024-06-20 optim.tex
sec 3 update text

\begin{keyword}
    projection pursuit \sep Jellyfish Search Optimiser (JSO) \sep 
    Optimisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, frame hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

The jellyfish optimiser (JSO) mimics the natural movements of jellyfish,
which include passive and active motions driven by ocean currents and
their swimming patterns, respectively. In the context of optimization,
these movements are abstracted to explore the search space in a way that
balances exploration (searching new areas) and exploitation (focusing on
promising areas). The algorithm aims to find the optimal solution by
adapting the jellyfish's behaviour to navigate towards the best solution
over iterations \citep{chou_novel_2021}.

To understand what the jellyfish optimizer is doing in the context of
Projection Pursuit, we first start with a current projection (the
starting point). Then, we evaluate this projection using an index
function, which tells us how good the current projection is. We then
move the projection in a direction determined by the `best jelly' and
random factors, influenced by how far along we are in the optimization
process (the trial \(i\) and \texttt{max.tries}). Occasionally, we might
explore completely new directions like a jellyfish might with ocean
currents. Then, we compare new potential projections to our current one.
If they're better, we adopt them; if not, we stick with our current
projection. This process continues and iteratively improves the
projection, until we reach the maximum number of trials.

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toptitle=1mm, breakable, colbacktitle=quarto-callout-note-color!10!white, leftrule=.75mm, left=2mm, titlerule=0mm, colframe=quarto-callout-note-color-frame, coltitle=black, opacitybacktitle=0.6, colback=white, toprule=.15mm, bottomtitle=1mm, arc=.35mm, bottomrule=.15mm, opacityback=0]

>>>>

\begin{keyword}
    projection pursuit \sep Jellyfish Search Optimiser (JSO) \sep 
    Optimisation
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

JSO mimics the natural movements of jellyfish, which include passive and
active motions driven by ocean currents and their swimming patterns,
respectively. In the context of optimization, these movements are
abstracted to explore the search space in a way that balances
exploration (searching new areas) and exploitation (focusing on
promising areas). The algorithm aims to find the optimal solution by
adapting the behaviour of jellyfish to navigate towards the best
solution over iterations \citep{chou_novel_2021}.

To solve the optimisation problem embedded in the PP guided tour, a
starting projection, an index function and the maximum number of
iterations are provided as input. Then, the current projection is
evaluated by the index function. The projection is then moved in a
direction determined by a random factor, influenced by how far along we
are in the optimization process. Occasionally, we might explore
completely new directions like a jellyfish might with ocean currents. A
new projection is accepted if it is an improvement compared to the
current one, rejected otherwise. This process continues and iteratively
improves the projection, until the pre-specified maximum number of
trials is reached.

\begin{tcolorbox}[enhanced jigsaw, toptitle=1mm, colframe=quarto-callout-note-color-frame, titlerule=0mm, opacitybacktitle=0.6, colback=white, left=2mm, coltitle=black, bottomrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, toprule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, rightrule=.15mm, opacityback=0]
